\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-01 paper.qmd
Added descriptions reagrding the best fit

@fig-scurve-sc-best shows one of the best fits for S-curve data. TriMAP with $15$ nearest neighbors for forming the nearest neighbor triplet (`n_inliers`), $3$ outliers for forming the nearest neighbor triplets (`n_outliers`), $3$ random triplets per point (`n_random`).

@@

Model in \gD{}, on the TriMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, and it adequately captures the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/zEz2MUCtADM>). 
:::

>>>>

@fig-scurve-sc-best shows one of the best fits for S-curve data. TriMAP with $15$ nearest neighbors for forming the nearest neighbor triplet (`n_inliers`), $3$ outliers for forming the nearest neighbor triplets (`n_outliers`), $3$ random triplets per point (`n_random`) is used as the NLDR method. The model is generated with $103$ bins, which have a width of $0.154$ and a height of $0.133$. Edges with lengths greater than $0.266$ are removed.

@@

Model in \gD{}, on the TriMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has twists. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/zEz2MUCtADM>). 
:::

### 2024-07-01 paper.tex
Added descriptions reagrding the best fit

Figure~\ref{fig-scurve-sc-best} shows one of the best fits for S-curve
data. TriMAP with \(15\) nearest neighbors for forming the nearest
neighbor triplet (\texttt{n\_inliers}), \(3\) outliers for forming the
nearest neighbor triplets (\texttt{n\_outliers}), \(3\) random triplets
per point (\texttt{n\_random}).

@@

\caption{\label{fig-scurve-sc-best}Model in \gD{}, on the TriMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, and it adequately
captures the surface. (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
(\url{https://youtu.be/zEz2MUCtADM}).}

>>>>

Figure~\ref{fig-scurve-sc-best} shows one of the best fits for S-curve
data. TriMAP with \(15\) nearest neighbors for forming the nearest
neighbor triplet (\texttt{n\_inliers}), \(3\) outliers for forming the
nearest neighbor triplets (\texttt{n\_outliers}), \(3\) random triplets
per point (\texttt{n\_random}) is used as the NLDR method. The model is
generated with \(103\) bins, which have a width of \(0.154\) and a
height of \(0.133\). Edges with lengths greater than \(0.266\) are
removed.

@@

\caption{\label{fig-scurve-sc-best}Model in \gD{}, on the TriMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has twists. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at (\url{https://youtu.be/zEz2MUCtADM}).}
